Non-word repetition in Yélî Dnye

### 2020-09-09 manuscript.tex

%% Pandoc can only set 10, 11, 12 pt
%% uncomment below to set fontsize
%\usepackage[fontsize=13pt]{scrextend}

%\setmainfont{Calibri} % Set main font for latin characters

\setlength{\parskip}{0.15cm} % Set space between paragraphs
%\linespread{1.2}\selectfont % Set line height
%\usepackage[doublespacing]{setspace} % Use double space without changing footnotes line height

%% Special font for IPA
%% Make sure "Doulos SIL" is installed on your computer
%% For other typefaces supporting IPA symbols, see
%% https://en.wikipedia.org/wiki/International_Phonetic_Alphabet#Typefaces
\newfontfamily\ipa{Doulos SIL} % Font for IPA symbols
\DeclareTextFontCommand{\ipatext}{\ipa}

%%%         Section for CJK Characters                   %%%
%%%   You may want to uncomment the code below if        %%%
%%%   you're writing this document with CJK characters   %%%

%\usepackage{xeCJK}  % Uncomment for using CJK characters
%% Set main font for CJK characters
%% Make sure your system has the font set
%\setCJKmainfont[
%	BoldFont={HanWangHeiHeavy}  % Set font for CJK boldface
%    ]{標楷體}    % Set font for normal CJK
%% Some Traditional Chinese fonts: AR PL KaitiM Big5, PingFang TC, Noto Sans CJK TC
%\XeTeXlinebreaklocale "zh"
%\XeTeXlinebreakskip = 0pt plus 1pt

@@

The Yélî sound system, much like its baroque grammatical system in
general ({\textbf{???}}), is unlike any other in the region, with 90
contrastive segments, including at least two contrasts not yet been
documented elsewhere (labial-coronal double-articulations with dental
vs.~post-alveolar coronal placement in both oral and nasal stops)
({\textbf{???}}). With only four primary places of articulation
(bilabial, alveolar, post-alveolar, and velar) and no voicing contrasts,
the phonological inventory is remarkably packed with acoustically
similar segments. The core oral stop set includes both singleton (/p/,
/t/, /ṭ/, and /k/) and doubly-articulated (/tp/, /ṭp/, /kp/) segments,
with full nasal equivalents (/m/, /n/, /ṇ/, /ŋ/, /nm/, /ṇm/, /ŋm/), and
with a substantial portion of these able to be pre-nasalized or nasally
released (/mp/, /nt/, /ṇṭ/, /ŋk/, /nmtp/, /ṇmṭp/, /ŋmkp/, /ṭṇ/, /kŋ/,
/ṭpṇm/, /kpŋm/). Finally, a number of these can also be labialized or
palatalized on the release, or both (/pʲ/, /tʃ/, /tpʲ/, /ṭʲ/, /ṭpʲ/,
/kʲ/, /kpʲ/, /pʲʷ/, /mbʲ/, /ndʒ/, /nmdbʲ/, /ṇḍʲ/, /ṇmḍbʲ/, /mbʷ/, /ŋɡʷ/,
/mbʲʷ/, /ṭṇʲ/, /ṭpṇmʲ/, /kŋʷ/, /mʲ/, /nʲ/, /nmʲ/, /ṇʲ/, /ṇmʲ/, /mʷ/,
/ŋʷ/, mʲʷ/). Among the remaining consonants are small group of oral
continuants (/w/, /j/, /ɣ/, /l/, /βʲ/, /lʲ/, /lβʲ/). Vowels in Yélî Dnye
may be oral or nasal, short or long. The 10 oral vowel qualities (/i/,
/ɯ/, /u/, /e/, /o/, /ə/, /ɛ/, /\ipatext{ɔ}/, /æ/, /ɑ/) can be produced
as short or long vowels, with 7 of these able to appear as short and
long nasal vowels as well (/i/, /u/, /ə/, /ɛ/, /\ipatext{ɔ}/, /æ/, /ɑ/).
In total, Levinson ({\textbf{???}}) then counts 90 distinctive segments
in Yélî Dnye (93 when including consonants that are extremely rarely
used).

@@

\caption{\label{tab:tab2-stims}NWR stimuli in orthographic and phonological representations.}
\centering
\begin{tabular}[t]{llllllllll}
\toprule
\multicolumn{2}{c}{Practice} & \multicolumn{2}{c}{Monosyll} & \multicolumn{2}{c}{Bisyll} & \multicolumn{2}{c}{Trisyll} & \multicolumn{2}{c}{Tetrasyll} \\
\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
Orth. & Phon. & Orth. & Phon. & Orth. & Phon. & Orth. & Phon. & Orth. & Phon.\\
\midrule
nopimade & ṇɔpimædɛ & dp:a & ṭpæ͂ & kamo & kæmɔ & dimope & ṭimɔpɛ & diponate & ṭipɔṇætɛ\\
poni & pɔṇi & dpa & ṭpæ & kani & kæṇi & diyeto & ṭijɛtɔ & nomiwake & ṇɔmiwækɛ\\
wî & wɯ & dpâ & ṭpɑ & kipo & kipɔ & meyadi & mɛjæṭi & todiwuma & tɔṭiwumæ\\
 &  & dpê & ṭpə & noki & ṇɔki & mituye & mitujɛ & wadikeno & wæṭikɛṇɔ\\
 &  & dpéé & ṭpe: & nomi & ṇɔmi & nademo & ṇædɛmɔ &  & \\
\addlinespace
 &  & dpi & ṭpi & piwa & piwæ & nayeki & ṇæjɛki &  & \\
 &  & dpu & ṭpu & towi & tɔwi & nuyedi & ṇujɛdi &  & \\
 &  & gh:ââ & ɣɑ: & tupa & tupæ & pedumi & pɛdumi &  & \\
 &  & ghuu & ɣu: &  &  & tiwune & tiwuṇɛ &  & \\
 &  & kp:ââ & kpɑ͂: &  &  & tumowe & tumɔwɛ &  & \\
\addlinespace
 &  & kpu & kpu &  &  & widone & wiṭɔṇɛ &  & \\
 &  & lv:ê & lβʲə &  &  & wumipo & wumipɔ &  & \\
 &  & lva & lβʲæ &  &  &  &  &  & \\
 &  & lvi & lβʲi &  &  &  &  &  & \\
 &  & t:êê & tə͂ː &  &  &  &  &  & \\
\addlinespace
 &  & tp:a & tpæ͂ &  &  &  &  &  & \\
 &  & tpâ & tpɑ &  &  &  &  &  & \\
 &  & tpê & tpə &  &  &  &  &  & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\setmainfont{Doulos SIL} % Set main font to Doulos SIL

@@

The Yélî sound system, much like its baroque grammatical system in
general ({\textbf{???}}), is unlike any other in the region, with 90
contrastive segments, including at least two contrasts not yet been
documented elsewhere (labial-coronal double-articulations with dental
vs.~post-alveolar coronal placement in both oral and nasal stops)
({\textbf{???}}). With only four primary places of articulation
(bilabial, alveolar, post-alveolar, and velar) and no voicing contrasts,
the phonological inventory is remarkably packed with acoustically
similar segments. The core oral stop set includes both singleton (/p/,
/t/, /ṭ/, and /k/) and doubly-articulated (/tp/, /ṭp/, /kp/) segments,
with full nasal equivalents (/m/, /n/, /ṇ/, /ŋ/, /nm/, /ṇm/, /ŋm/), and
with a substantial portion of these able to be pre-nasalized or nasally
released (/mp/, /nt/, /ṇṭ/, /ŋk/, /nmtp/, /ṇmṭp/, /ŋmkp/, /ṭṇ/, /kŋ/,
/ṭpṇm/, /kpŋm/). Finally, a number of these can also be labialized or
palatalized on the release, or both (/pʲ/, /tʃ/, /tpʲ/, /ṭʲ/, /ṭpʲ/,
/kʲ/, /kpʲ/, /pʲʷ/, /mbʲ/, /ndʒ/, /nmdbʲ/, /ṇḍʲ/, /ṇmḍbʲ/, /mbʷ/, /ŋɡʷ/,
/mbʲʷ/, /ṭṇʲ/, /ṭpṇmʲ/, /kŋʷ/, /mʲ/, /nʲ/, /nmʲ/, /ṇʲ/, /ṇmʲ/, /mʷ/,
/ŋʷ/, mʲʷ/). Among the remaining consonants are small group of oral
continuants (/w/, /j/, /ɣ/, /l/, /βʲ/, /lʲ/, /lβʲ/). Vowels in Yélî Dnye
may be oral or nasal, short or long. The 10 oral vowel qualities (/i/,
/ɯ/, /u/, /e/, /o/, /ə/, /ɛ/, /ɔ/, /æ/, /ɑ/) can be produced as short or
long vowels, with 7 of these able to appear as short and long nasal
vowels as well (/i/, /u/, /ə/, /ɛ/, /ɔ/, /æ/, /ɑ/). In total, Levinson
({\textbf{???}}) then counts 90 distinctive segments in Yélî Dnye (93
when including consonants that are extremely rarely used).

@@

\caption{\label{tab:tab2-stims}NWR stimuli in orthographic and phonological representations.}
\centering
\begin{tabular}[t]{llllllllll}
\toprule
\multicolumn{2}{c}{Practice} & \multicolumn{2}{c}{Monosyll} & \multicolumn{2}{c}{Bisyll} & \multicolumn{2}{c}{Trisyll} & \multicolumn{2}{c}{Tetrasyll} \\
\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
Orth. & Phon. & Orth. & Phon. & Orth. & Phon. & Orth. & Phon. & Orth. & Phon.\\
\midrule
nopimade & nɔpimæṭɛ & dp:a & ṭp̃æ & kamo & kæmɔ & dimope & ṭimɔpɛ & diponate & ṭipɔnætɛ\\
poni & pɔni & dpa & ṭpæ & kani & kæni & diyeto & ṭijɛtɔ & nomiwake & nɔmiwækɛ\\
wî & wɯ & dpâ & ṭpɑ & kipo & kipɔ & meyadi & mɛjæṭi & todiwuma & tɔṭiwumæ\\
 &  & dpê & ṭpə & noki & nɔki & mituye & mitujɛ & wadikeno & wæṭikɛnɔ\\
 &  & dpéé & ṭpeː & nomi & nɔmi & nademo & næṭɛmɔ &  & \\
\addlinespace
 &  & dpi & ṭpi & piwa & piwæ & nayeki & næjɛki &  & \\
 &  & dpu & ṭpu & towi & tɔwi & nuyedi & nujɛṭi &  & \\
 &  & gh:ââ & ɣ̃ɑː & tupa & tupæ & pedumi & pɛṭumi &  & \\
 &  & ghuu & ɣuː &  &  & tiwune & tiwunɛ &  & \\
 &  & kpu & kpu &  &  & tumowe & tumɔwɛ &  & \\
\addlinespace
 &  & lv:ê & lβʲ̃ə &  &  & widone & wiṭɔnɛ &  & \\
 &  & lva & lβʲæ &  &  & wumipo & wumipɔ &  & \\
 &  & lvi & lβʲi &  &  &  &  &  & \\
 &  & tp:a & tp̃æ &  &  &  &  &  & \\
 &  & tpâ & tpɑ &  &  &  &  &  & \\
\addlinespace
 &  & tpê & tpə &  &  &  &  &  & \\
\bottomrule
\end{tabular}
\end{table}
